\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage{multicol}
    \setlength{\multicolsep}{-3.0pt}
    \setlength{\columnsep}{-1pt}
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {José A. Davila-Ciullo}}\\
	  www.buhdashexclamationpoint.com \textbar{} jsdvlcll@gmail.com $\cdot$ 469-389-9800\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Stanford University}\hfill Stanford, CA\\
Bachelors: Computer Science (Systems focus) \textit{GPA: 3.7} \hfill Sept 2020 - March 2025 \\
\vspace{2.5mm}

%------RELEVANT COURSEWORK-------
\header{Relevant Coursework}
\vspace{1mm}    
        \begin{multicols}{5}
            \begin{itemize}
                \setlength\itemsep{1mm}
                \item Operating Systems
                \item Computer Networking
                \item Compilers
                \item Computer + Network Security
                \item Advanced Cryptography
                \item Blockchain Technology
                \item Web Development
                \item Designing Serious Games
                \item Rusty Systems
                \item Feminist Games Studio
            \end{itemize}
        \end{multicols}
        \vspace{3mm}
    %\resumeSubHeadingListEnd
    
%==== Experience ====%
\header{Work Experience}
\textbf{Tinuiti} \hfill Remote\\
\textit{Software Engineer II} \hfill May 2025 - Present\\
\begin{itemize} \itemsep 1pt
    \item Designed a DuckDB-WASM-powered analytics platform to power our cross-channel metrics system, eliminating server fetch times and enabling real-time chart updates without more backend calls.
    \item Built a matching frontend component library including redesigned charts and tables, allowing users to create customized analytics dashboards with granular control now that our data was right in their browser.
    \item Recruited as an intern and was later offered a full-time role. Now on the data engineering team, primarily writing Go, Java, and SQL.
\end{itemize}
\textbf{Stanford Computer Science Department} \hfill Stanford, CA\\
\textit{CS106A/B Teaching Assistant} \hfill March 2024 - April 2025\\
\begin{itemize} \itemsep 1pt
    \item Led weekly hour-long sections for 10+ students in Stanford's Programming Methodology/Abstractions courses, reinforcing concepts covered in lectures through engaging examples and group problem-solving.
    \item Provided detailed feedback on student assignments weekly, identifying common misconceptions and individually guiding them to improve their understanding.
    \item Held weekly office hours and LaIR to help students debug their assignments and answer any of their CS, university, life questions.
\end{itemize}
\textbf{Youth Alliance for Housing} \hfill New York City, NY\\
\textit{Full Stack Dev/Security Zine Producer} \hfill Jun 2022 - Present\\
\begin{itemize} \itemsep 1pt
	\item Designed and developed the organization's central website (y4h.org) using SvelteKit and StoryBlok to share their initiatives and accrue new members.
    \item Currently continue my involvement with the organization as a member and sole maintainer of the website's repo.
\end{itemize}
\textbf{Canyons Rock Climbing Gym} \hfill Dallas, TX\\
\textit{Event Manager/Climbing Instructor/Desk} \hfill Jun 2019 - Aug 2021\\
\begin{itemize} \itemsep 1pt
	\item Directed gym community events including birthdays, lock-ins, climbing competitions, etc.
	\item Managed front-desk operations, new member registrations/belaying lessons, and liability waivers.
	\item Ran and managed kids climb with two other coworkers.
\end{itemize}
\header{Skills}
\vspace{1mm}
\begin{tabular}{ l l }
	Programming Languages: & C/C++, Zig, Go, Rust, Java, Lua, Python, SQL, frontend stuff\\
    Areas of Interest: & Game development, ECS, network/computer security, P2P protocols, fediverse
\end{tabular}\\
\end{document}